\documentclass[a4paper,12pt]{report}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{caption}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    citecolor=blue
}

% Header and Footer Setup
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Security Risk Assessment}
\fancyhead[R]{TactiCore AI}
\fancyfoot[C]{\thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% Section Formatting
\titleformat{\chapter}{\normalfont\LARGE\bfseries}{\thechapter}{1em}{}
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\large\bfseries}{\thesubsection}{1em}{}

% Document Information
\title{Security Risk Assessment Report}
\author{TactiCore AI Security Team}
\date{\today\ at 10:13 PM KST}

\begin{document}

\maketitle
\thispagestyle{empty}
\clearpage

\tableofcontents
\clearpage

\chapter{Introduction}
\section{Overview}
Creating comprehensive overview identifying assessing securing critical assets within TactiCore AI infrastructure. This report outlines potential security risks associated with document and route planning systems deployed on September 26, 2025.

\section{Scope}
Covering all digital assets including audit logs, route data, and user authentication systems located in Santo Domingo operations center.

\chapter{Risk Identification}
\section{Identified Risks}
Listing risks discovered during initial assessment process:
\begin{itemize}[leftmargin=*]
    \item Unauthorized access to sensitive route data.
    \item Tamper attempts on audit logs detected at 10:07 PM KST.
    \item Potential data breaches due to unencrypted transmissions.
\end{itemize}

\chapter{Risk Assessment}
\section{Risk Evaluation}
Evaluating severity and likelihood using table format:
\begin{longtable}{|p{4cm}|p{3cm}|p{3cm}|p{3cm}|}
\hline
\textbf{Risk} & \textbf{Severity} & \textbf{Likelihood} & \textbf{Impact Score} \\ \hline
Unauthorized Access & High & Medium & 8 \\ \hline
Tamper Attempts & Medium & High & 7 \\ \hline
Data Breaches & High & Low & 6 \\ \hline
\end{longtable}

\chapter{Mitigation Strategies}
\section{Proposed Actions}
Implementing following actions reducing identified risks:
\begin{itemize}[leftmargin=*]
    \item Encrypting all data transmissions using AES-256.
    \item Deploying real-time tamper detection with multi-channel alerts.
    \item Conducting regular security audits scheduled for October 10, 2025.
\end{itemize}

\chapter{Conclusion}
\section{Summary}
Concluding current security posture considered adequate following implementation proposed mitigation strategies. Continuous monitoring recommended ensuring long-term security.

\end{document}
